---
title: '`hgwellsr` package'
author: "Yap S S"
date: "17/11/2020"
output:
  word_document: default
  html_document:
    df_print: paged
---

### Goal
The goal of `hgwellsr` package is to provides access to the full texts of 6 novels by H. G. Wells. The plain-text for each novel was sourced and lightly cleaned from Project Gutenberg. Each novel is in a character vector. Currently, the package contains: 

- timemachine: The Time Machine, (1895) 

#### WIP
- annveronica : Ann Veronica, (1909) 
- mrpolly : The History of Mr Polly, (1910) 
- invisibleman : The Invisible Man, (1897) 
- doctormoreau : The Island of Doctor Moreau, (1896) 
- waroftheworlds : The War of the Worlds, (1898) 

### Install my package as follows
```{r}
library(devtools)
install_github("mryap/hgwellsr")
```


### The War of the Worlds, (1898)
```{r}
library(hgwellsr) # load library
waroftheworlds
```

### The Time Machine, (1895) 
```{r}
library(hgwellsr) # load library
timemachine
```
### Hire Yap

Web Analytics: Google Analytics, Google Tag Manager, Google API, Google Data Studio, Google Optimize

Google Marketing Data warehouse : Extract insights from diverse datasets into Google BigQuery (up to 324GB) with sql query as part of a hands-on lab skill in From Data to Insights with Google Cloud Platform

Web Design/Development: HTML, CSS, JavaScript

Advanced MS Excel: Vlookup, Index, Match, pivot tables

Machine Learning Algorithms: Decision Trees, Logistic Regression, Multiple Linear Regression, K Means Clustering, Random Forest

Data Science: R and Python for data collection (API, database, JSON), data parsing & cleaning, analysis in RMarkdown/Jupyter Notebooks, Docker and Conda for portability and reproducibility, Terminal/Shell command line for GitHub version control 

Framework: Understand "See-Think-Do-Care" Customer Journey Mapping for marketing, HEART for product development process, Jobs-To-Be-Done for customer and Fogg Behavior Model
